Theories of deliberated choice

### 2024-05-13 simple.tex
Conj seems okay

  A counter-example could be a situation where exactly one individual given $\emptyset$ chooses $\phi$, with the claim: “there is at most one individual who given $\emptyset$ chooses $\phi$”.
  Nope, this seems to admit a claim about types, as then there is finitely many individuals satisfying $\emptyset$ to $\phi$ and hence some of these functions can be excluded.

>>>>

  In other words, we look for, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, a possible observable that is not compatible with any ${\allleadsto} \circ \sigma$.

  To prove the conjecture, given $\allleadsto$ satisfying $\forall \hist \in \allhists: P^{\intvl{\hist}} \wsub \restr{{\allleadsto}(I)}{\intvl{\hist}}$, consider any observable whatsoever, $O \in \allpriobss$, and let us show that for some bijection $\sigma$ over $I$, $O \wsub ({\allleadsto} \circ \sigma)$.

  A counter-example could be a situation “at most one of each possible behavior”.
  Nope: if there’s twice the same behavior, we cannot observe it for sure.
